Preprocing and mergind datasets

### 2022-12-03 Old scripts/intero_study_preprocessing.Rmd
test for Review
recover the power analyses files

BiocManager::install("rhdf5")
library(rhdf5)

@@

list.of.packages <- c("ggplot2", "data.table", 'readr', "c", 'tidyverse', "gazer", 'lmerTest')
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]

# if(length(new.packages)) install.packages(new.packages)
lapply(list.of.packages, require, character.only = TRUE)
# lapply(new.packages, require, character.only = TRUE)

# install.packages('devtools')

@@

# 2021 data
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021")
hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021"

@@

# gp extractor function
takes gp files and returns a clean files with messages parsed and deletes unnecessary stuff

Starting from 322 we have gsr v and hr v. and Pulse is around the 30

@@

Problem files
```{r}
# 355  - did not finish IAPS
# adjust below manually

  hdfFilesList = list.files(hdf5FilesPath, pattern = "\\.hdf5$")
  hdfFilesList
  if (length(hdfFilesList) == 0){

    return(message('No HDF5 files found in the directory provided.'))
  }
   f = 10# adjust here to the index for the probematic file
  for (f in 1:length(hdfFilesList)) {

    #ATTTENTIONNN  note this sometimes fails because we are using a notebook 
    # Extract Events from hdf5, in that case run it from command
    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')

    unique(tmp.events$screencontent)

    # tmp.eyetr_backup<- tmp.eyetr
    # tmp.df_backup<- tmp.df
    # tmp.df<- tmp.df_backup
    colnames(tmp.df)
    # rm(tmp.raw.trial)
    # colnames(tmp.raw.trial)
    colnames(tmp.df)
    colnames(tmp.events1)
    colnames(tmp.eyetr)
    tmp.df$screencontent<- NA
    tmp.df$stim<- NA
    # e=10
    tmp.events1$tEnd<- if_else(tmp.events1$tNo == -7, tmp.events1$tStart+120, tmp.events1$tEnd)
    message(sprintf("subsetting eyetracking data"))
    e=1
    for(e in 1:nrow(tmp.events1)) {

# tmp_full<- gp.extractor(hdf5FilesPath)

# for some reason 355 is creating duplicate event ids
library(readr)
ss355_GPdata_ <- read_csv("ss355_GPdata .csv")

View(ss355_GPdata_)

ss355_GPdata_nodup <- subset(ss355_GPdata_, !duplicated(ss355_GPdata_$event_id))

write_csv(ss355_GPdata_nodup, "ss355_GPdata_nodup.csv")

now cleaning
we need to have data for ledalab
gaze path
clean and trackloss

@@

# now read them
# setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021/step1")

@@

```{r}
library(tidyverse)
colnames(tmp.df2)
tmp.df3<- tmp.df2

@@

# let's check to see if it looks fine - NOTE THIS IS a bit SLOW
ggplot(tmp.df3, aes(time, gsr, colour = as.factor(ssid)))+
  geom_line()
  # facet_grid(~screencontent)

@@

# fill up
   tmp.df3<- tmp.df3%>%
      arrange(time)%>%
     group_by(ssid, tNo)%>%
      fill(zero_stim, .direction = c('up'))

tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim
   # check timerezero2

@@

#tmp.df3<- subset(tmp.df3, is.na(tmp.df3$ssid) == FALSE)
tmp.df3%>%
subset(Condition == 'IAPS' & ssid ==  353)%>%
  ggplot(aes(x = timerezero3, y= gsr))+
  stat_smooth()+
    # geom_smooth()+
    # geom_()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

tmp.df3%>%
subset( tNo == -5)%>%
  ggplot( aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

natest<- subset(tmp.df3, is.na(tmp.df3$tNo) == TRUE)

tmp.df3<- subset(tmp.df3, is.na(tmp.df3$tNo) == FALSE)

@@

```{r}

tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo,time)
# gsr baseline wil be the 1 second before tial start
# gsr to microsiemnes 1/J3*100000

options(scipen = 999)

tmp.df3$gsr_ms<- 1/tmp.df3$gsr*100000
unique(tmp.df3$ssid)
max(tmp.df3$gsr_ms)
min(tmp.df3$gsr_ms)

@@

unique(db_GSR$Condition)

db_GSR$Condition2<- if_else(db_GSR$Condition == 'Rest', 'Rest', 'IAPS')
unique(db_GSR$Condition2)
db_GSR$split_column<- paste0(db_GSR$Condition2,paste(db_GSR$ssid))
unique(db_GSR$split_column)
  (sprintf("writing for ledlab"))

@@

# baselining gsr
```{r}
# use ms to baseline
tmp.df3_backup<- tmp.df3

@@

tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo, gsr_bastrue)%>%
  mutate(gsr_bas_median = median(gsr_bas))

@@

tmp.df3_backup<- tmp.df3
# gsr respone
tmp.df3$gsr_resp_Log<- if_else(tmp.df3$timerezero3 > 1,TRUE, FALSE)
unique(tmp.df3$gsr_resp_Log)

@@

# gsr response for every bit
unique(tmp.df3$screencontent)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo, screencontent)%>%
  mutate(gsr_response_scrcont =   max(gsr_basCor))

@@

tmp.df3<-
  tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response)

tmp.df3<-
  tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response,  .direction = c('up'))

@@

tmp.df3_backup<- tmp.df3
```

@@

```{r}
library(gazer)

min(tmp.df3$pupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

@@

tmp.df3_backup <- tmp.df3

# note that smothing and interpolating is order dependednt so order by ssid, trial and time
tmp.df3<- tmp.df3 %>%
  arrange(ssid, trialUnq,tNo, time)%>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

@@

# library(gazer)

?smooth_interpolate_pupil

# vert order dependent
tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

# tmp.df3<- tmp.df3 %>%
#   group_by(ssid, trialUnq,tNo,screencontent) %>%
#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
#                                     extendblinks=TRUE, 
#                            step.first= 'smooth',
#                                     maxgap=10, 
#                                     filter = 'moving',
#                                     type="linear", hz=20, n = 10)
# 
# 
# tmp.df3<-
#   tmp.df3%>%
#   arrange(ssid,tNo,time)
#   # group_by(ssid, tNo, timerezero3)%>%
# 
# tmp.df3te<- tmp.df3 %>%
#   group_by(ssid, Condition,tNo,screencontent) %>%
#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
#                                     extendblinks=TRUE, 
#                            step.first= 'smooth',
#                                     maxgap=Inf, 
#                                     filter = 'moving',
#                                     type="linear", hz=100, n = 5)

@@

subset(tmp.df3, tNo == 20 & ssid == 347)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  geom_line(aes(y = pupil), colour = 'gray')
  # facet_grid(~Condition)

subset(tmp.df3, tNo == -7 & ssid == 350)%>%
ggplot(aes(x = timerezero3, y= pupil))+
  geom_line()

subset(tmp.df3, tNo == 1)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  # geom_line(aes(y = pup_interp), colour = 'gray')+
    facet_grid(~ssid)
  # facet_grid(~Condition)
```

# create baseline pupil mean
```{r}
tmp.df3backup<- tmp.df3
tmp.df3$pup_bas<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, tmp.df3$pup_interp, NULL)
# true if bseline if baseline within widnown
tmp.df3$pup_bastrue<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, TRUE, FALSE)

@@

# do baseline correction
tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo, time)%>% # pay attentipn to order
  group_by(ssid, tNo)%>%
  mutate(pup_basCor = pup_interp - pup_bas_med)

@@

# MAD removal
library(gazer)
max_pup<-tmp.df3 %>%
  dplyr::group_by(subject, trial) %>%
  dplyr::mutate(speed=speed_pupil(pup_interp,time)) %>%
  dplyr::mutate(MAD=calc_mad(speed))
  # dplyr::filter(speed < MAD)

@@

ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
```
unique(tmp.df3$ssid)

```{r}
ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
    geom_smooth(se = T)+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

```{r}
colnames(tmp.df3)
table(is.na(tmp.df3$gsr_ms))
table(is.na(tmp.df3$hr))

@@

min(tmp.df3$hr, na.rm = TRUE)
max(tmp.df3$hr, na.rm = TRUE)

tmp.df3$hrv<- as.double(tmp.df3$hrv)
tmp.df3$hrv2<- if_else(is.na(tmp.df3$hrv) == TRUE, 999,tmp.df3$hrv)

@@

table(is.na(tmp.df3$hr_clean))
# interpolate, only 2 seconds 
library(zoo)

tmp.df3<- tmp.df3%>%
  arrange(ssid,tNo, time)

@@

  min(tmp.df3$hr, na.rm = TRUE)
ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 352) , aes(x = timerezero3, y= hr_interp))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_clean), linetype = 'dashed', colour = 'green', size = 0.3)+
   geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
    # geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    # geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

```{r}
tmp.df3 <- tmp.df3 %>%
    group_by(ssid, tNo, gsr_resp_Log, screencontent)%>%
    mutate(gsr_response_bycond =   max(gsr_basCor))

@@

# check to see this is right
ggplot(subset(tmp.df4, tmp.df3$ssid == 353) , aes(x = tNo, y= hr_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

ggplot(subset(tmp.df4, tmp.df3$ssid == 354) , aes(x = tNo, y= gaze_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = gaze_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

>>>>

BiocManager::install("rhdf5")

@@

list.of.packages <- c("ggplot2", "data.table", 'readr', "rhdf5", 'tidyverse', "gazer", 'lmerTest')
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
lapply(list.of.packages, require, character.only = TRUE)
lapply(new.packages, require, character.only = TRUE)

install.packages('devtools')

@@

@@

# gp extractor function
takes gp files and returns a clean files with messages parsed and deletes unecessary stuff

Starting from 322 we have gsr v and hr v. And OPulse is around the 30

@@

now cleaning
we need to have data for ledalab
gaze path
clean and tracloss

@@

# now read them
setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")

@@

```{r}
colnames(tmp.df2)
tmp.df3<- tmp.df2

@@

# let's check to see if it looks fine
ggplot(tmp.df3, aes(time, gsr, colour = as.factor(ssid)))+
  geom_line()
  # facet_grid(~screencontent)

@@

# fill up
   tmp.df3<- tmp.df3%>%
      arrange(time)%>%
     group_by(ssid, tNo)%>%
      fill(zero_stim, .direction = c('up'))
   tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim
   # check timerezero2

@@

#tmp.df3<- subset(tmp.df3, is.na(tmp.df3$ssid) == FALSE)

ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
    geom_smooth()+
    # geom_()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tmp.df3$tNo == -4) , aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

natest<- subset(tmp.df3, is.na(tmp.df3$tNo) == TRUE)
tmp.df3<- subset(tmp.df3, is.na(tmp.df3$tNo) == FALSE)

@@

```{r}
tmp.df3<- tmp.df3%>%
  arrange(ssid, time,tNo)
# gsr baseline wil be the 1 second before tial start
# gsr to microsiemnes 1/J3*100000

options(scipen = 999)
tmp.df3$gsr_ms<- 1/tmp.df3$gsr*100000
unique(tmp.df3$ssid)
max(tmp.df3$gsr_ms)
min(tmp.df3$gsr_ms)

@@

unique(db_GSR$Condition)
db_GSR$Condition2<- if_else(db_GSR$Condition == 'Rest', 'Rest', 'IAPS')
unique(db_GSR$Condition2)
db_GSR$split_column<- paste0(db_GSR$Condition2,paste(db_GSR$ssid))
unique(db_GSR$split_column)
  (sprintf("writing for ledlab"))

@@

# baselining gsr
```{r}
# use ms to baseline

@@

tmp.df3<- tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo, gsr_bastrue)%>%
  mutate(gsr_bas_median = median(gsr_bas))

@@

# gsr respone
tmp.df3$gsr_resp_Log<- if_else(tmp.df3$timerezero3 > 1,TRUE, FALSE)
unique(tmp.df3$gsr_resp_Log)

@@

# gsr response for every bit
unique(tmp.df3$screencontent)
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo, screencontent)%>%
  mutate(gsr_response_scrcont =   max(gsr_basCor))

@@

tmp.df3<-
  tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response)

tmp.df3<-
  tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response,  .direction = c('up'))

@@

@@

```{r}
library(gazer)
min(tmp.df3$pupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

@@

tmp.df3<- tmp.df3 %>%
  group_by(ssid, trialUnq) %>%
  mutate(extendpupil=extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

@@

library(gazer)

tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

@@

ggplot(subset(tmp.df3, tmp.df3$tNo == 10 & tmp.df3$ssid == 320) , aes(x = timerezero3, y= pup_interp, colour = as.factor(ssid)))+
  geom_line()+
  geom_line(aes(y = pupil), colour = 'gray')
  # facet_grid(~Condition)

# create baseline pupil mean
tmp.df3backup<- tmp.df3
tmp.df3$pup_bas<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, tmp.df3$pup_interp, NULL)
# true if bseline if baseline within widnown
tmp.df3$pup_bastrue<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, TRUE, FALSE)

@@

# do baseline correction
tmp.df3<- tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo)%>%
  mutate(pup_basCor = pup_interp - pup_bas_med)

@@

# MAD removal
max_pup<-tmp.df3 %>%
  dplyr::group_by(subject, trial) %>%
  dplyr::mutate(speed=speed_pupil(pup_interp,time)) %>%
  dplyr::mutate(MAD=calc_mad(speed))
  # dplyr::filter(speed < MAD)

@@

ggplot(subset(tmp.df3, tmp.df3$tNo == 5 & tmp.df3$ssid == 900) , aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

unique(tmp.df3$ssid)

ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
    geom_smooth(se = T)+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

colnames(tmp.df3)
table(is.na(tmp.df3$gsr_ms))
table(is.na(tmp.df3$hr))

@@

min(tmp.df3$hr, na.rm = TRUE)
max(tmp.df3$hr, na.rm = TRUE)
tmp.df3$hrv<- as.double(tmp.df3$hrv)
tmp.df3$hrv2<- if_else(is.na(tmp.df3$hrv) == TRUE, 999,tmp.df3$hrv)

@@

table(is.na(tmp.df3$hr_clean))
# interpolate, only 2 seconds 
library(zoo)
tmp.df3<- tmp.df3%>%
  arrange(ssid, time, tNo)

@@

  min(tmp.df3$hr, na.rm = TRUE)
ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 320) , aes(x = timerezero3, y= hr_interp))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_clean), linetype = 'dashed', colour = 'green', size = 0.3)+
   geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
    # geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    # geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

tmp.df3 <- tmp.df3 %>%
    group_by(ssid, tNo, gsr_resp_Log, screencontent)%>%
    mutate(gsr_response_bycond =   max(gsr_basCor))

@@

# check to see this is right
ggplot(subset(tmp.df4, tmp.df3$ssid == 324) , aes(x = tNo, y= hr_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

ggplot(subset(tmp.df4, tmp.df3$ssid == 324) , aes(x = tNo, y= gaze_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = gaze_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
